---
title: "shiny.likert"

---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## 📂 Data

### 1. CSV from Google sheets & Google Form
- `shiny.likert` was developed in consideration of Google Sheets. However, accessing sheet using `googlesheets4` package requires some **Auth** problem which may induce security problem. 
- So, `shiny.likert` accepts CSV file (downloaded)

You can check [pre-built form](https://docs.google.com/forms/d/e/1FAIpQLScLLoQCpbP45XEGqFlv7TA1FozQoac6DMk0Gmi9mH0ru4cGYQ/viewform) and it's [data](https://github.com/zarathucorp/shiny.likert/blob/main/Test%20Survey%20Data(Response).csv).(download it)

This data is consisted with 3 columns. 

1. Timestamp (When user submited survey)
2. Multiple choice question (from **Strongly agree** to **Strongly disagree**)

### 2. Example data from `likert` package

Since `shiny.likert` utilize [`likert`](https://github.com/jbryer/likert) package, you can use this data as tutorial. but still you should save it as **csv file**.

```{r}
library(likert)
data("pisaitems")
write.csv(pisaitems[,2:5], file = 'pisaitems.csv', row.names = FALSE)
```

Since full dataset of pisaitem has large size (for shinyapps) we'll only try for some column


## 🕹️ Run application

```{r setup, eval=FALSE}
library(shiny.likert)

shiny.likert() # Run shiny application
```

With this code, you can run shiny application. 

If you run this in browser like chrome (rathen than rstudio viewer), UI layout will be little better (`shiny.likert` developed in chrome environment)

Below is step to generate likert chart.

1. Upload your csv file
2. Select column to visualize
  - **NOTE** You should select columns with same range variable.
  - For example, column 1 consisted with `A` ~ `E`, and column 2 is consisted with `Good` ~ `Bad`
  you can only select one of them. or app will not work properly
  
3. Order the variables, (**Bad option** goes into **Top**)
4. `Draw` button
5. Customize chart options.
6. Save the image 

